### 2013-11-08 research/paper/results/results-2.3.tex
uploaded 10.23 November 8th

At \reynoldsnumber=22300 two major phenomena was present. The maximum of the mean power tend to increase  as the $m^*$ was decreased while keeping the $U^*$ constant (Fig\ref{fig:mstarcollapsed_parkinson}(a)). The same effect was observed when $U^*$ was increased keeping $m^*$ constant (\ref{fig:mstarcollapsed_parkinson}(b)). It should be noted that the influence of $U^*$ was observed only for low mass ratios.  The velocity time traces of example cases of both scenarios Fig.\ref{time_history_mstar} and \ref{time_history_mstar} shows that essentially the same \hilight{phenomenon} occurring in both cases whereby the velocity signal tend to move towards a square from a sinusoidal signal.

@@

In this paper, the power transfer of a square body under aero elastic galloping is analysed by solving the quasi-steady state model equations through numerical integration. The power output of the system is not dependent on \ustar or natural frequency of the system, but dependent on the transverse velocity amplitude of the system. This is shown by the collapsed plots in terms of non-dimensionalised damping constant (using flow parameters). By analysing key regions of the power vs \ustar curve it could be concluded that in order to obtain an optimum power output, the damping constant ($\frac{c}{\rho\mathcal{A}U}$) should be high, but not excessive until it  to hinders the galloping from reaching induced angles of attack where the forcing is significant.

>>>>

At \reynoldsnumber=22300 two major phenomena could be observed. The maximum of the mean power tend to increase  as the $m^*$ was decreased while keeping the $U^*$ constant (Fig\ref{fig:mstarcollapsed_parkinson} (a)). The same effect was observed when $U^*$ was increased keeping $m^*$ constant (\ref{fig:mstarcollapsed_parkinson} (b)). It should be noted that the influence of $U^*$ was observed only for low mass ratios.  The velocity time traces of example cases of both scenarios Fig.\ref{time_hostory_mstar_mass} and \ref{time_history_mstar_ustar} shows that essentially the same \hilight{phenomenon} occurring in both cases whereby the velocity signal tend to move towards a square from a sinusoidal signal. The displacement signal tend to become more triangular. the reason behind the increase in power while reducing mass ratio is due to the fact that the inertia of the system becomes low. Therefore the body accelerate faster and attains higher velocity quickly. Therefore the time period where the body sustains high velocity increases which will lead to an increase in time period where the body in influenced by the higher forcing, which leads to a higher power output. As for the case to where the mean power increases with increasing $U^*$ for a given low mass ratio, the exploration tend to be similar where the only difference being that the at high $U^*$ the period of oscillation tend to increase therefore the body sustains higher velocities for a longer time leading to a higher power output.

@@

In this paper, the power transfer of a square body under aero elastic galloping is analysed by solving the quasi-steady state model equations through numerical integration. The power output of the system is not dependent on \ustar or natural frequency of the system, but dependent on the transverse velocity amplitude of the system. This is shown by the collapsed plots in terms of non-dimensionalised damping constant (using flow parameters). By analysing key regions of the power vs \ustar curve it could be concluded that in order to obtain an optimum power output, the damping constant ($\frac{c}{\rho\mathcal{A}U}$) should be high, but not excessive until it  to hinders the galloping from reaching induced angles of attack where the forcing is significant. The effect of mass ratio was could also be observed where at \reynoldsnumber=165 the mean power tend to decrease at $m^*<40$ which was found out to be an influence of vortex shedding. At \reynoldsnumber=22300 an opposite result could be observed where the mean power tend to increase with decreasing mass ratio as well as the mean power tend to increase with increasing $U^*$ at low mass ratios. The cause for this was found out to be the fact that as the mass ratios decreases the due to the lower inertia the velocity sinusoidal signal tend to move towards a square signal where it sustains high velocities for longer periods of time which leads to a higher mean power output.
